---
title: "Data Visualization - 8. Polishing and Presenting Plots"
author: "Kieran Healy"
date: "`r Sys.Date()`"
output: kjhslides::kjh_slides_reader
editor_options: 
  chunk_output_type: console
---

```{r note, include=FALSE}
## NB: By default the  template will create a new subdirectory with its files inside.
```


```{r packages, include=FALSE}
library(flipbookr)
library(here)
library(tidyverse)
library(kjhslides)
```


```{r setup, include=FALSE}
## Configure the slides

kjh_register_tenso()    # Default fonts. Comment out if you don't have Tenso and Berkeley fonts.
kjh_set_knitr_opts()    
kjh_set_slide_theme()   # ggplot theme to go with slides. Set tenso = FALSE if necessary.
kjh_set_xaringan_opts()

```



class: center middle main-title section-title-1

# .kjh-yellow[Polishing] & .kjh-lblue[Presenting] your Plots 

.class-info[

**Data Wrangling: Session 8**

.light[Kieran Healy<br>
Code Horizons, April 2022
]

]


---

layout: true
class: title title-1

---

# Load our libraries

```{r 03a-dplyr-basics-2, message = FALSE}
library(here)       # manage file paths
library(tidyverse)  # your friend and mine
library(socviz)     # data and some useful functions
library(ggrepel)    # Text and labels
library(colorspace) # luminance-balanced palettes
library(ggforce)    # useful enhancements to ggplot
```


---

class: center middle main-title section-title-1

# .huge[.kjh-yellow[Piece by piece,]<br/>.kjh-lblue[Layer by layer]]

---

# Build your plots a piece at a time

```{r}
asasec <- as_tibble(asasec)
asasec
```

---

# Build your plots a piece at a time

```{r, echo = FALSE, fig.height=8, fig.width=12}
asasec |> 
  filter(Year == 2014) |> 
  ggplot(mapping = aes(x = Members, 
                       y = Revenues, 
                       label = Sname)) + 
  geom_smooth() + 
  geom_point()

```

---

# Build your plots a piece at a time

```{r, echo = FALSE, fig.height=8, fig.width=12}
asasec |> 
  filter(Year == 2014) |> 
  ggplot(mapping = aes(x = Members, 
                       y = Revenues, 
                       label = Sname)) + 
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray60") +
  geom_point(mapping = aes(color = Journal), 
             size = rel(3)) + 
  geom_text_repel(data=subset(asasec,
                    Year == 2014 & 
                    Revenues > 7000),
                    size = rel(5), 
                    mapping = 
                    aes(family = "Tenso Slide")) + 
  scale_y_continuous(labels = 
                       scales::dollar_format()) + 
  labs(x="Membership", y="Revenues",
        color = "Section has own Journal",
        title = "ASA Sections",
        subtitle = "2014 Calendar year.",
        caption = "Source: ASA annual report.") + 
  theme(legend.position = "bottom")
  

```


---
`r chunk_reveal("reveal-asasteps", widths = c(40,60), title = "# Build your plots a piece at a time")`

```{r reveal-asasteps, include = FALSE}
asasec |> 
  filter(Year == 2014) |> 
  ggplot(mapping = aes(x = Members, 
                       y = Revenues, 
                       label = Sname)) + 
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray60") +
  geom_point(mapping = aes(color = Journal), 
             size = rel(3)) + 
  geom_text_repel(data=subset(asasec,
                    Year == 2014 & 
                    Revenues > 7000),
                    size = rel(5), 
                    mapping = 
                    aes(family = "Tenso Slide")) + 
  scale_y_continuous(labels = 
                       scales::dollar_format()) + 
  labs(x="Membership", y="Revenues",
        color = "Section has own Journal",
        title = "ASA Sections",
        subtitle = "2014 Calendar year.",
        caption = "Source: ASA annual report.") + 
  theme(legend.position = "bottom")

```
---

class: center middle main-title section-title-1

# .huge[.kjh-lblue[More about Scales]]

```{r, echo = FALSE}
kjh_set_classic_theme()
```

---

# Working with .kjh-yellow[`color`] and .kjh-pink[`fill`] scales

- .center.large[.kjh-green[`scale\\\_`].kjh-orange[`<MAPPING>`].kjh-green[`\\\_`].kjh-lblue[`<KIND>`].kjh-green[`()`]]

- .large[Scale functions control the display of the variables they map. So to change the colors for `color` or `fill` mappings, you adjust the corresponding .kjh-green[`scale_`] function, not the .kjh-green[`theme()`] function.] 

- .large[.kjh-lblue[`ggplot`] has several color palettes built in. A variety of packages provide others.] 

---
`r chunk_reveal("reveal-scalemanual", widths = c(35,65), title = "# You can always specify scales manually")`

```{r reveal-scalemanual, include = FALSE}
p <- ggplot(data = organdata,
            mapping = aes(x = roads, 
                          y = donors, 
                          color = world)) + 
  geom_point(size = 4)

p

```

---
`r chunk_reveal("reveal-scalemanual2", widths = c(35,65), title = "# You can always specify scales manually")`

```{r reveal-scalemanual2, include = FALSE}
p + scale_color_manual(
  values = c("red", "green", "blue"))

```


---
`r chunk_reveal("reveal-scalemanual3", widths = c(35,65), title = "# You can always specify scales manually")`

```{r reveal-scalemanual3, include = FALSE}
p + scale_color_manual(
  values = c("#1B9E77","#D95F02", "#7570B3"))

```


---
`r chunk_reveal("reveal-scalemanual4", widths = c(35,65), title = "# You can always specify scales manually")`

```{r reveal-scalemanual4, include = FALSE}

colkey <- c("Corporatist" = "pink", 
            "Liberal" = "goldenrod", 
            "SocDem" = "firebrick")
colkey

p + scale_color_manual(
  values = colkey)

```

---

# But many balanced palettes are available


