---
title: "Index"
author: "Kieran Healy"
date: '2022-05-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(tidyverse))
suppressMessages(library(here))
```

```{r, echo = FALSE}
fnames <- fs::dir_ls(here::here("slides"), recurse = 1, glob = "*.html") |> 
  fs::path_file() |> 
  as_vector()

fpath <- fs::dir_ls(here::here("slides"), recurse = 1, glob = "*.html") |> 
  fs::path_dir() |> 
  as_vector()

#tibble::tibble(a = fnames, b =fpath, c = fnames)


```

## Items

- [01-looking-at-data.html](01-looking-at-data/01-looking-at-data.html)   
- [02-about-r.html](02-about-r/02-about-r.html)                       
- [03-make-a-graph.html](03-make-a-graph/03-make-a-graph.html)                  
- [04-show-the-right-numbers.html](04-show-the-right-numbers/04-show-the-right-numbers.html)        
- [05-work-with-dplyr-and-geoms.html](05-work-with-dplyr-and-geoms/05-work-with-dplyr-and-geoms.html)     
- [06-work-with-models.html](06-work-with-models/06-work-with-models.html)              
- [07-make-maps.html](07-make-maps/07-make-maps.html)                     
- [08-polishing-and-presenting-plots.html](08-polishing-and-presenting-plots/08-polishing-and-presenting-plots.html)
- [09-case-studies.html](09-case-studies/09-case-studies.html)                  
 
