---
title: "Data Visualization"
description: |
  A Short Course using R and the Tidyverse suite of tools.
author:
- name: Kieran Healy
  url: https://kieranhealy.org
date: "`r Sys.Date()`"
output: distill::distill_article
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<hr>

# Information for Participants

This page contains information for seminar participants. Please read it and follow the instructions below to download and install the necessary software and course materials.

# The Course Packet

[Click here to download the course packet as a zip file.](https://github.com/kjhealy/data_visualization_notes/archive/refs/heads/main.zip) See below for more details.

# Course Overview

### Sign-up and Registration

- Learn more about logistical and registration information at the [seminar's home page at Code Horizons](https://codehorizons.com/Seminars/data-visualization/)

This course will teach you how to think about good data visualization, and how to do it. We begin with some core principles about how we see graphs, what makes some of them better than others, and how to begin cultivating good judgment about visualization. Then, through a series of worked examples, you will learn how to use ggplot to make graphs piece by piece. The emphasis throughout is on acquiring a practical feel for and good judgement about the way ggplot can be used, from the simplest cases to sophisticated, highly customized data visualizations.

### Learning objectives

The effective use of graphs and charts is an important way to explore data for yourself and to communicate your ideas and results to others. Being able to produce effective plots from data is also the best way to develop an eye for reading and critically understanding visualizations made by others, whether presented in academia, business, policy, or the media. Learning how to visualize data effectively is more than just knowing how to write code that produces figures from data. This course will teach you how to do that. But it will also teach you how to think about the information you want to show, and how best to present it to your audience—including when the audience is yourself.

### Is this course for me?

You should take this workshop if:

1. You want to understand the basic principles behind effective data visualizations, and how they are implemented in R and ggplot.
2. You want to better develop your practical sense for why some graphs and figures work well while others do not.
3. You want to feel more confident and fluent in ggplot, in order to make, refine, and effectively present good data visualizations.

# Before the Course Begins

We will be working with the most recent stable versions of R and RStudio, as well as with a number of additional packages. You will need to install R, RStudio, and the necessary packages on your own computer.

### Install R and RStudio on your Laptop

- Begin by installing R (<http://cloud.r-project.org>). Choose the version appropriate for your computing platform:
  - [macOS with an Apple Silicon (M-series) processor](https://cran.r-project.org/bin/macosx/big-sur-arm64/base/R-4.5.0-arm64.pkg)
  - [macOS with an Intel processor](https://cran.r-project.org/bin/macosx/big-sur-x86_64/base/R-4.5.0-x86_64.pkg)
  - [Windows](https://cran.r-project.org/bin/windows/base/R-4.5.0-win.exe), 
  - [Linux](https://cloud.r-project.org/bin/linux/).
- Next, install RStudio (<https://posit.co/download/rstudio-desktop/>). Follow the links under "2: Install RStudio" to download the free RStudio Desktop edition recommended for your system.

### Install the required additional Packages

- Once the applications are installed, launch RStudio. Either carefully type in or copy-and-paste the following lines of code at R’s command prompt, located in the RStudio window named “Console”, and then hit return. In the code below, the <- arrow is made up of two keystrokes, first < and then the short dash or minus symbol, -.

```R
## Code to run at the RStudio console begins here

my_packages <- c("tidyverse", "broom", "cowplot", 
                  "drat", "gapminder", "GGally", "ggforce", 
                  "ggrepel", "ggraph", "ggridges", "graphlayouts", 
                  "here", "marginaleffects", "maps", "mapproj", 
                  "mapdata", "MASS", "modelsummary", "naniar", "palmerpenguins", 
                  "patchwork", "prismatic", "quantreg", "remotes", 
                  "scales", "sf", "socviz", "survey", "srvyr", 
                  "tidygraph")

install.packages(my_packages, repos = "http://cran.rstudio.com")

data_packages <- c("covdata", "congress", "kjhnet", "nycdogs", "uscenpops")
remotes::install_github(data_packages)

## Code to run ends here

```

GitHub is a software development platform and service that is widely used by R Developers. You can [read some background on it from an R user's point of view here](https://happygitwithr.com/big-picture.html).

If you do not have one already, it will be useful to create a GitHub account and obtain a GitHub Personal Access Token. This is _not required_ for the course, but would be helpful to have. After you have installed R and RStudio, to get set up, read and _carefully follow_ the instructions here:

- Register a [GitHub Account](https://happygitwithr.com/github-acct.html)
- Install [Git](https://happygitwithr.com/install-git) and a [Git Client](https://happygitwithr.com/git-client.html)
- Get a [Personal Access Token](https://happygitwithr.com/https-pat)
- Connect to [GitHub](https://happygitwithr.com/push-pull-github.html)

Again, setting up a GitHub account is _not required_ to fully participate in the course.



### Download the Course Packet

The [course packet](https://github.com/kjhealy/data_visualization_notes/archive/refs/heads/main.zip) can be downloaded as a zip file: [click here to download it](https://github.com/kjhealy/data_visualization_notes/archive/refs/heads/main.zip). It is an RStudio project containing PDFs of the slides for the course together with code for almost all of the graphs we will draw, along with a starter file for your course notes, some additional datasets we may use, and other material. After you have installed R and RStudio, download the course packet and uncompress it on your computer. (If you are on Windows _make sure the zip file is actually uncompressed_ by right-clicking on it and selecting "Extract All".) Once the packet is uncompressed into a folder named `data_visualization_notes`, double-clicking the file inside that folder named `data_visualization_notes.Rproj` should launch the project in RStudio.

# The Course Slack

During the seminar we will use a [Slack](https://slack.com) to provide an additional channel of communication outside the lectures. You will recieve details about how to sign up prior to the course. I encourage you to use the Slack to ask questions, share code snippets, and discuss matters arising in the seminar, from "I can't get this to work" troubleshooting on up to any other more general comments or queries about the material we are covering.

